Here are some popular developer tools (DevTools) that are widely used for web development:

1. **Chrome DevTools**: Built into the Google Chrome browser, it provides a suite of tools for inspecting HTML and CSS, debugging JavaScript, analyzing performance, and more.

2. **Firefox Developer Tools**: Integrated into the Firefox browser, these tools offer similar functionalities to Chrome DevTools, including a JavaScript debugger, CSS grid and flexbox inspectors, and network monitoring.

3. **Safari Web Inspector**: Available in the Safari browser, this tool allows developers to inspect and debug web pages, view network requests, and analyze performance.

4. **Microsoft Edge DevTools**: Built into the Microsoft Edge browser, these tools provide features for debugging, profiling, and optimizing web applications.

5. **React Developer Tools**: A browser extension for Chrome and Firefox that allows developers to inspect the React component hierarchy, view props and state, and measure performance.

6. **Redux DevTools**: A tool for debugging Redux applications, allowing developers to inspect every action and state change in their application.

7. **Postman**: A popular tool for testing APIs, allowing developers to send requests, inspect responses, and automate API testing.

8. **Fiddler**: A web debugging proxy that logs all HTTP(S) traffic between your computer and the internet, allowing you to inspect and modify requests and responses.

9. **Lighthouse**: An open-source tool integrated into Chrome DevTools that audits web pages for performance, accessibility, SEO, and best practices.

10. **WebPageTest**: An online tool that allows developers to test the performance of their web pages from different locations and browsers, providing detailed reports on load times and performance metrics.

These tools can significantly enhance the development, debugging, and optimization processes for web applications.